### 2004-08-09 Documentation/part2.tex
Added the the information how to terminate a user-defined smearin matrix in AEDL (page 81)

The energy smearing matrix $K_{ij}$ has {\tt \$bins} rows and {\tt \$sampling\_points} columns, which are numbered from $0$ to {\tt \$bins}$-1$ or {\tt \$sampling\_points}$-1$. It is equivalent to the 
bin- and sampling-point-based kernel in \eq~(\ref{eq:kernel}):
\begin{equation}
K_{ij} = K_i^c(E) |_{E=E_j},
\label{equ:ematrix}
\end{equation}
where $E_j$ is the energy of the $j$th sampling point. In general, many of the entries in this matrix are zero, which means that it is convenient to evaluate the integrand in \eq~(\ref{eq:simple_int}) only at positions where
$K_{ij}$ is non-zero. The corresponding ``sampling range'' range of non-zero matrix entries  in $K_{ij}$ for the $i$th energy bin is defined to run from
column $k_l^i$ (``lower index'') to column $k_u^i$ (``upper index'').
An example for a smearing matrix is
\begin{equation}
K_{ij} =   \underbrace{ \left( \begin{array}{cccccccccc} 
a_{00} & a_{01} & a_{02} & a_{03} &  &  &  &  &  & \\
a_{10} & a_{11} & a_{12} & a_{13} & a_{14} &  &  &  &  &  \\
 & a_{21} & a_{22} & a_{23} & a_{24} & a_{25} &  &  &  &  \\
 &  & a_{32} & a_{33} & a_{34} & a_{35} & a_{36} &  &  &  \\
 &  &  & a_{43} & a_{44} & a_{45} & a_{46} & a_{47} &  &  \\
& & & \uparrow  & & \ddots & & \uparrow & & \\
& & & k_l^i & & & & k_u^i & & \\ 
\end{array}\right) }_{\mathtt{\$sampling\_points}  \, \, \mathrm{columns}} \quad \leftarrow \quad \footnotesize{\mathtt{\$bins} \, \, \mathrm{rows}} \, ,
\end{equation}
where the unshown entries are zero. Thus, the values of $K_{ij}$ have to be specified between $k_l^i$ and $k_u^i$ in the form $\{ k_l^i,k_u^i, K_{i \, k_l^i}, K_{i k_l^i+1} , \hdots , K_{i k_u^i} \}$:
\index{aedl}{{\tt energy}!energy@{\tt "@energy}}
\begin{quote}
{\tt 
energy(\#name)<\\
\tb @energy =   \{0,2, 0.8634265, 0.0682827,     4e-06\}:\\
\tb\tb \{0,4, 0.1507103, 0.6965592, 0.1507103,   0.00101,     1e-07\}:\\
\tb\tb $\ldots$\\
>
}
\end{quote}
Note that the sum of all entries in each {\em column} should be equal 
to unity,
since all of the incoming neutrinos should be assigned to energy bins. In many practical cases, however, the definition of the energy smearing can
lead to sums smaller than unity, such as in the case of truncated Gau\ss ian
distributions. The sum of entries in each {\em row} is not defined, since the events might be unevently distributed into the energy bins
according to the energy resolution function.

>>>>

The energy smearing matrix $K_{ij}$ has {\tt \$bins} rows and {\tt \$sampling\_points} columns, which are numbered from $0$ to {\tt \$bins}$-1$ or {\tt \$sampling\_points}$-1$. It is equivalent to the 
bin- and sampling-point-based kernel in \eq~(\ref{eq:kernel}):
\begin{equation}
K_{ij} = K_i^c(E) |_{E=E_j},
\label{equ:ematrix}
\end{equation}
where $E_j$ is the energy of the $j$th sampling point. In general, many of the entries in this matrix are zero, which means that it is convenient to evaluate the integrand in \eq~(\ref{eq:simple_int}) only at positions where
$K_{ij}$ is non-zero. The corresponding ``sampling range'' range of non-zero matrix entries  in $K_{ij}$ for the $i$th energy bin is defined to run from
column $k_l^i$ (``lower index'') to column $k_u^i$ (``upper index'').
An example for a smearing matrix is
\begin{equation}
K_{ij} =   \underbrace{ \left( \begin{array}{cccccccccc} 
a_{00} & a_{01} & a_{02} & a_{03} &  &  &  &  &  & \\
a_{10} & a_{11} & a_{12} & a_{13} & a_{14} &  &  &  &  &  \\
 & a_{21} & a_{22} & a_{23} & a_{24} & a_{25} &  &  &  &  \\
 &  & a_{32} & a_{33} & a_{34} & a_{35} & a_{36} &  &  &  \\
 &  &  & a_{43} & a_{44} & a_{45} & a_{46} & a_{47} &  &  \\
& & & \uparrow  & & \ddots & & \uparrow & & \\
& & & k_l^i & & & & k_u^i & & \\ 
\end{array}\right) }_{\mathtt{\$sampling\_points}  \, \, \mathrm{columns}} \quad \leftarrow \quad \footnotesize{\mathtt{\$bins} \, \, \mathrm{rows}} \, ,
\end{equation}
where the unshown entries are zero. Thus, the values of $K_{ij}$ have to be specified between $k_l^i$ and $k_u^i$ in the form $\{ k_l^i,k_u^i, K_{i \, k_l^i}, K_{i k_l^i+1} , \hdots , K_{i k_u^i} \}$:
\index{aedl}{{\tt energy}!energy@{\tt "@energy}}
\begin{quote}
{\tt 
energy(\#name)<\\
\tb @energy =   \{0,2, 0.8634265, 0.0682827,     4e-06\}:\\
\tb\tb \{0,4, 0.1507103, 0.6965592, 0.1507103,   0.00101,     1e-07\}:\\
\tb\tb $\ldots$\\
\tb\tb \{40,42, 0.1507103, 0.6965592, 0.1507103\};\\
>
}
\end{quote}
The last line has to be terminated by a semicolon `;'.
Note that the sum of all entries in each {\em column} should be equal 
to unity,
since all of the incoming neutrinos should be assigned to energy bins. In many practical cases, however, the definition of the energy smearing can
lead to sums smaller than unity, such as in the case of truncated Gau\ss ian
distributions. The sum of entries in each {\em row} is not defined, since the events might be unevently distributed into the energy bins
according to the energy resolution function.
